Creating optimal conditions for reproducible data analysis in R with `fertile`

### 2020-02-29 fertile.Rmd
edits to conclusion

Unlike with many other R packages focused on reproducibility that are currently available, the features of **fertile** can be accessed almost effortlessly, making it easy for data analysts of all skill levels and backgrounds to gain a better understanding of how to make their work reproducible. Many of **fertile**'s features can be accessed in only two lines of code and using minimal arguments, and some of the proactive features can be accessed purely upon loading the package. As a result, it is beneficial to a wide audience--simple enough to be used by students in an introductory data science course, but still helpful to experienced analysts.

**fertile** is designed to educate the user about why the mistakes are problematic and how to fix them, promoting a greater understanding of reproducibility concepts in its users.

**fertile** also addresses a human challenge of reproducibility. In the moment, it often feels easiest to take a shortcut---to use an absolute path or change a working directory. However, when considering the long term path of a project, spending the extra time to improve reproducibility is worthwhile. **fertile**'s user-friendly features can help data analysts avoid these harmful shortcuts with minimal effort.

>>>>

**fertile** is meant to be educational, providing informative error messages showing how the ways in which the mistakes the user is making are problematic, as well as sharing recommendations on how to fix them. The package is designed in this way so as to promote a greater understanding of reproducibility concepts in its users, with the goal of increasing the overall awareness and understanding of reproducibility in the R community.

The package has very low barriers to entry, making it accessible to users with various levels of background knowledge. Unlike with many other R packages focused on reproducibility that are currently available, the features of **fertile** can be accessed almost effortlessly. Many of the retroactive features can be accessed in only two lines of code requiring  minimal arguments, and some of the proactive features can be accessed with no additional effort beyond loading the package. This, in combination with the fact that **fertile** does not focus on one specific area of reproducibility, instead covering (in less detail) a wide variety of topics, means that **fertile** makes it easy for data analysts of all skill levels to quickly gain a better understanding of the reproducibility of the work.

In the moment, it often feels easiest to take a shortcut---to use an absolute path or change a working directory. However, when considering the long term path of a project, spending the extra time to improve reproducibility is worthwhile. **fertile**'s user-friendly features can help data analysts avoid these harmful shortcuts with minimal effort.
